The problem and promise of scale in multilayer animal social networks

### 2020-02-15 paper/manuscript.Rmd
weak

<!--
how to combine moving forward
in areas of high selection/low selection or favorable/unfavorable habitat
combined with seasonality

in our case study, we looked at increase spatial scales of landcover metrics

we could define layers of the multilayer network according to home range overlap 
instead of specific associations
looking at broader temporal scales and coarser spatial resolutions
-->

Multilayer networks can be used to explicitly consider habitat selection and
sociality across scales. Animal social systems can be parsed by spatial
contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
The effect of resource phenology can be directly measured by differences in
habitat selection and sociality across temporal layers. Habitat selection can be
explicitly integrated using network layers defined by similarity of selection
coefficients between individuals. These explicit integrations of habitat
selection and sociality across social, spatial and temporal scales highlight the
potential for novel insights from multilayer networks.

>>>>

<!-- TODO: weak -->
Multilayer networks can be used to explicitly consider habitat selection and
sociality across scales. Animal social systems can be parsed by spatial
contexts, defined, for example, by habitat types as in Figure \@ref(fig:lcres).
The effect of seasonality of resources can can be directly measured by differences in
habitat selection and sociality across temporal layers. Habitat selection can be
explicitly integrated using network layers defined by similarity of selection
coefficients between individuals. These explicit integrations of habitat
selection and sociality across social, spatial and temporal scales highlight the
potential for novel insights from multilayer networks.
